### 2018-07-03 pack/prv/opt/tokipona/aux/article/acm/samplebody-journals.tex
terminada revisao do artigo de toda a parte de syntax highlighting

The considerable irrelevance of the morphosyntactic classes as
described in Section~\ref{syntax} suggests that an appropriate coloring
of words should
either distinguish only between particles, prepositions and the rest,
or consider the syntax to identify the nouns, verbs, adjectives, adverbs,
prepositions and particles.
Also, the coloring for poems might be more appealing if considered
e.g. the counting of syllables, the repeated letters or syllables,
and the ending syllables.
Insights might be obtained through the
choices made and advocated in software such as text editors
(e.g. Vim, Emacs, Sublime),
packages dedicated to syntax highlighting (e.g.
pigments\footnote{\url{http://pygments.org/docs/}} and 
highlight.js\footnote{\url{https://highlightjs.org/}},
and
other software (e.g. Linux terminals such as Xterm and gnome-terminal).
Finally, the careful choice of fonts is known to have
a relevant impact in comfort and productivity~\cite{fonts},
e.g. sans-sheriff fonts are more promptly read and yield a cleaner
text than a serif font, and the same applies to a monospaced font
which is more likely to yield a cleaner text, at least for programming.

One might also 
consider the mapping the textual structures
to sound~\cite{mass} (i.e. parametrize the synthesis of sounds e.g. 
by the counting of specific tokens inside a script, a function or
class or around a variable of conditional or
loop), which might be called ``syntax sonification''.

>>>>

The considerable irrelevance of the morphosyntactic classes,
described in Section~\ref{syntax}, suggests that an appropriate coloring
of words should
either distinguish only between particles, prepositions and the rest,
or consider the syntax to identify the nouns, verbs, adjectives, adverbs,
prepositions and particles.
Also, the coloring of poems might be more appealing if considered
e.g. the counting of syllables, the repeated letters or syllables,
and the ending syllables.
Further insights might be obtained through the
choices made and advocated in software such as text editors
(e.g. Vim, Emacs, Sublime),
packages dedicated to syntax highlighting (e.g.
pigments\footnote{\url{http://pygments.org/docs/}} and 
highlight.js\footnote{\url{https://highlightjs.org/}}),
and
other software (e.g. Linux terminals such as Xterm and gnome-terminal).
Finally, the careful choice of fonts is known to have
a relevant impact in comfort and productivity~\cite{fonts},
e.g. sans-sheriff fonts are more promptly read and yield a cleaner
text than a serif font, and the same applies to a monospaced font
which is more likely to yield a cleaner text, at least for programming.
One might also 
consider the mapping the textual structures
to sound~\cite{mass} (i.e. parametrize the synthesis of sounds e.g. 
by the counting of specific tokens inside a script, a function or
class or around a variable of conditional or
loop), which might be called ``syntax sonification''.
